Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-24 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model. We compare this model with a promising QoS-aware model, and also compare our PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.

@@

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service compositions are considered to be less efficient while automated web service composition has less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to QoS. This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing one of challenges above. Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value. In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarities.

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together.

 \item To evaluate our proposed approach, we conduct experiments to compare our comprehensive quality model with one widely used QoS evaluation model. We also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model. Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of a graph is minimised to reach the optimised graph-based composition solutions. However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. but there exists a scalability problem for the enumeration technique. EC tecQoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}hniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimse a queue of task related services that is decoded into composition solutions. We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.

@@

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, \textit{manual and semi-automated web service compositions} are considered to be less efficient while \textit{automated web service composition} demands less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic dimension enables a better underrstanding and collaboration through ontology-based semantics \cite{o2005review}. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services. The second challenge is related to finding optimised solutions in QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.

Existing works on service composition focus mainly on addressing only one challenge above. Among these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow. This is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}. Meanwhile, many research works consider the NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desired balance.

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously to achieve a desirable balance on both sides.

 \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model. To do that we optimise a queue of web services by evaluating its decoded representations. These representations are the solutions for semantic web service composition.

 \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our propopsed model with one widely used QoS model using PSO-based approach. In addtion, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model. Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.
